Comparative study of Dask and Spark for neuroimaging pipelines\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Natural Sciences and Engineering Research Council}

### 2019-06-26 latex/paper.tex

\subsubsection{PySpark RDD~\cite{spark-rdd}} Spark is a general-purpose Big Data
framework. It provides in-memory computing, data locality, and lazy evaluation. Spark
abstracts resilient distributed dataset (RDD)~\cite{RDD} making it fault-tolerant.
Its high-level API provides optimizations for transformations applied data. Since
Spark is written in Scala, this optimization is lessened because it requires a
serialization from Python to Java. The API offered by Spark is flexible and suits
most problems however it differs from the Python ecosystem. The standalone scheduler
is used for our experiment. It has a LIFO policy.

@@

\subsubsection{Dask Delayed~\cite{dask-delayed}} Dask Delayed is a low-level API. It
does not offer the optimized algorithm as the high-level APIs however it allows the
user to parallelize custom function that does not fit in the array, dataframe or
MapReduce framework. This is perfect for the more complex functions which could
easily be parallelized. Like Dask Bag, it offers in-memory computing, data locality
and lacks fault resilience. The Dask Distributed scheduler is used.

@@

In Figure~\ref{fig:inc_tt_worker}, the y-axis shows the total execution time of the
incrementation application. The hatch indicates that the time is spent for: read,
compute, write, and overhead. Again, the color represents the frameworks. The
computing time stays similar when the number of workers increases. However, the IO
time and overhead increase proportionally to the number of workers.

@@

%% Sleep time
\subsection{Experiment 1: Sleep delay}
Figure~\ref{fig:inc_ms_sleep} shows the makespan of the incrementation algorithm for
different sleep delays. Spark is initially slower than the Dask APIs, however, it is
because faster when increasing the sleep time. Also, within the Dask APIs, Dask Bag
is slower than the other two but it is not considerable.

>>>>

\subsubsection{PySpark RDD~\cite{spark-rdd}} Spark is a general-purpose Big Data
framework. It provides in-memory computing, data locality, and lazy evaluation. Spark
abstracts resilient distributed dataset (RDD)~\cite{RDD} making it fault-tolerant.
Its high-level API provides optimization for transformations applied on data. Since
Spark is written in Scala, this optimization is lessened because it requires a
serialization from Python to Java. The API offered by Spark is flexible and suits
most problems however it differs from the Python ecosystem. The standalone scheduler
is used for our experiment. It has a LIFO policy.

@@

\subsubsection{Dask Delayed~\cite{dask-delayed}} Dask Delayed is a low-level API. It
does not offer the optimized algorithm as the high-level APIs however it allows the
user to parallelize custom function that does not fit in the array, dataframe or
MapReduce framework. This is perfect for the more complex functions which could
potentially be parallelized. Like Dask Bag, it offers in-memory computing, data
locality and lacks fault resilience. The Dask Distributed scheduler is also used.

@@

In Figure~\ref{fig:inc_tt_worker}, the y-axis shows the total execution time of the
incrementation application. The hatch indicates the total time spent for: read,
compute, write, and overhead. Again, the color represents the frameworks. The
computing time stays similar when the number of workers increases. However, the IO
time and overhead increase proportionally to the number of workers.

@@

%% Sleep time
\subsection{Experiment 1: Sleep delay}
Figure~\ref{fig:inc_ms_sleep} shows the makespan of the incrementation algorithm for
different sleep delays. Spark is initially slower than the Dask APIs, however, it is
faster when increasing the sleep delay. Also, within the Dask APIs, Dask Bag is
slower than the other two but it is not considerable.
